### 2014-12-03 fundamentals/impl.tex
more changes to outline and adding text/TODOs where needed as a result of reorg

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and mutiprocess execution on a number of platforms. This section begins by 
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software, dynamic libraries, and interchangeable agents. It then introduces
the specific framework of \Cyclus: the region-institution-facility hierarchy, handling
of resources and materials, the Cycamore library of agents, and the experimental toolkit.
These features provide a solid foundation on which to build an interconnected community 
of archetype developers with diverse backgrounds and simulation goals.

\subsection{Modular Architecture}
% Motivation for encapsulated plug-in architecture 
% enables ecosystem, ease of contribution across institutions
% enables myriad levels of simulation fidelity
% enables FC analyses that can compare ‘apples to apples'

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness \cite{citation_needed}. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. Consider a case in which an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors. A variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

\Cyclus implements an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it incorporates modern computing resources.  
Furthermore, \gls{ABM} provides a natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context, for example, an analyst can design an agent with reactor-related logic 
that is entirely independent from an agent with fuel fabrication-related 
logic. Defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

@@

@@

@@

Placeholder as a reminder to add more detail about this.

\subsection{Software Decisions}

\subsubsection{Framework Structure}
% (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)

\acrlong{ABM} is inherently object-oriented because agents represent 
discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
creates a set of key classes on which agent plug-ins 
are based. In addition, a set of key tools are also provided to enrich the 
\gls{API} and supply a robust suite of behaviors for the developer. 
Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on a paradigm of dynamic loading and clean plug-in 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

\subsection{Simulation Assistance}

>>>>

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and multiprocess execution on a number of platforms. This section begins by 
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework using an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
capabilities, is described, focusing on agent interchangeability and the 
implementation of the region-institution-facility heirarchy. 
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \TODO{DRE}.
Support for users and developers via the Cycamore library of
agents \TODO{archetypes?} and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.
These features provide a solid foundation on which to build an interconnected community 
of archetype developers with diverse backgrounds and simulation goals.

\subsection{Software Architecture}
% Motivation for encapsulated plug-in architecture 
% enables ecosystem, ease of contribution across institutions
% enables myriad levels of simulation fidelity
% enables FC analyses that can compare ‘apples to apples'

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness \cite{citation_needed}. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. For example, if an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors, a variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

\Cyclus implements an \acrlong{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it incorporates modern computing resources.  
Furthermore, \gls{ABM} provides a natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context, for example, an analyst can design an agent with reactor-related logic 
that is entirely independent from an agent with fuel fabrication-related 
logic. Defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

@@

% (OO, cpp, xml, backends, inheritances, mixins, generic apis, etc.)

\gls{ABM} is inherently object-oriented because agents represent 
discrete, independently acting objects.  Figure \ref{fig:framework} illustrates
the modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator 
creates a set of key classes on which agent plug-ins 
are based. In addition, a set of key tools are also provided to enrich the 
\gls{API} and supply a robust suite of behaviors for the developer. 
Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on a paradigm of dynamic loading and clean plug-in 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

@@

\TODO{AO Opinion: Move some of the detail from this intro to the main section
on discrete materials. Then add an intro to the discrete time/DRE as well.}

@@

\TODO{This is SO for you, Matt Gidden!}
Placeholder as a reminder to add more detail about this.

\subsection{Simulation Assistance}
\TODO{section intro needed}
To assist beginner users and developers in accomplishing working simulations
in the shortest time possible,
